Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-05-27 draft_p2.tex
Fix x label for figure IS_GKTL #4
Make colors for commands TL and EL less aggressive
Iteration de l'abstract par @tlestang #8

\newcommand{\EL}[1]{{\color{red}{#1}}}
\newcommand{\TL}[1]{{\color{green}{#1}}}

@@

\begin{abstract}
	\EL{ ABSTRACT TO BE REVIEWED \#8}
This study evaluates the relevance of  rare-event sampling to optimize the numerical simulation of extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body. The main idea is here to replace a long simulation by a set of much shorter simulations (running in parallel) with dynamics that are replicated or abandoned in order to sample large-amplitude events more frequently. 
%
Such technique has already proved its efficiency for simulating extreme events in {...} with significant run-time savings.
Application to fluid-structure interaction problems remains mainly open. 
%
The drag experienced by a squared obstacle placed in a turbulent flow (in two dimensions) is taken as a representative case study to investigate the performance of two major sampling algorithms, namely {...} 
Practical evidence is given that these algorithms allow for the correct sampling of rare large-amplitude drag events and the estimation of return times with a reduced computational effort. However, {limitations and pitfalls}. 
% Importantly, such techniques also provide direct access to the flow scenario yielding extreme events. In the present case, it is found that {<blocking effect>}.
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IS_GKTL/IS_GKTL}
	\caption{\label{fig:IS_GKTL} Rare-event sampling of the (zero-mean) time-averaged drag $\tilde F_T = F_T - \overline{F_T}$ with $T=10~\tau_c$; $\tau_c$ is the correlation time of the instantaneous drag. The shaded \ac{pdf}s are estimated from the biased ensemble resulting from the \ac{gktl} algorithm applied to $16384$ trajectories of duration $T_a=T$ with the cloning period $\tau=\tau_c/2$.
	The dashed line denotes the unbiased \ac{pdf} of $\tilde F_T$, \textit{i.e.} from direct sampling or with $k=0$ (no bias) in the \ac{gktl} algorithm.
\EL{$F_T-\overline{F_T}$ in the figure! \#4}}
\end{figure}

>>>>

\definecolor{myred}{HTML}{b30000}
\definecolor{mygreen}{HTML}{008000}
\newcommand{\EL}[1]{{\color{myred}{#1}}}
\newcommand{\TL}[1]{{\color{mygreen}{#1}}}

@@

\begin{abstract}
\TL{  This study evaluates the relevance of rare-event sampling type approaches to make accessible the numerical simulation of extreme mechanical efforts exerted by a turbulent flow impinging onto a bluff body.
  The main idea is here to replace a long simulation by a set of much shorter simulations, running in parallel, wich corresponding dynamics are replicated or pruned in order to sample large-amplitude events more frequently. 
%
  Such techniques have been shown to be efficient for a wide range of problems in statistical physics, computer science, biochemistry, enabling the simulation of events far from reach from brute force sampling approaches.
  Application to fluid-structure interaction problems remains mainly open. 
%
  The drag experienced by a squared obstacle placed in a turbulent flow (in two dimensions) is taken as a representative case study to investigate the performance of two major sampling algorithms, namely the \ac{ams} and the \ac{gktl} algorithms.
  Practical evidence is given that the fast sweeping time of fluid structures has a drastic influence on the efficiency of the sampling with both algorithms.
  While is is shown that the \ac{ams} resampling does not lead to rare trajectories with siginificant run-time savings, we illustrate that the \ac{gktl} algorithm allows for the simulation of extreme fluctuations of the time-averaged drag, as well as accurate computation of the associated statistics, for instance return times.}
\end{abstract}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IS_GKTL/IS_GKTL}
	\caption{\label{fig:IS_GKTL} Rare-event sampling of the (zero-mean) time-averaged drag $\tilde F_T = F_T - \overline{F_T}$ with $T=10~\tau_c$; $\tau_c$ is the correlation time of the instantaneous drag. The shaded \ac{pdf}s are estimated from the biased ensemble resulting from the \ac{gktl} algorithm applied to $16384$ trajectories of duration $T_a=T$ with the cloning period $\tau=\tau_c/2$.
	The dashed line denotes the unbiased \ac{pdf} of $\tilde F_T$, \textit{i.e.} from direct sampling or with $k=0$ (no bias) in the \ac{gktl} algorithm.}
\end{figure}
